Visualize ukb whole genome, s40.22

### 2020-11-04 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
SERI

Next, the analysis is done at the “region” level, which is 500kb bins along the genome. Each bin would contain all the SNPs, as well as all the genes in that bin. We are exploring several ways to select regions that contain true signals, e.g. based on regional sum of mr.ash PIP for genes/SNPs, region smallest TWAS p value for gene/SNPs, or regional bayes factors, etc.

@@

## Regions: all (1)

* Susie run parameters: `L=1`.  We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

@@

## Regions: all (2)

* Susie run parameters: `L=1`. We initialize with prior for genes and SNPs using their true values. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

```{r param2, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config2.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config2.susieI.txt")

@@

## Regions: causal

* Susie run parameters: `L=1`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

```{r param5, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config5.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config5.susieI.txt")

@@

## Regions: filtered (1)
* We filterd regions with regional minimum FDR of both genes and SNPs < 0.05, round 700 regions left.
* Susie run parameters: `L=1`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

```{r param3, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config3.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config3.susieI.txt")

## Regions: filtered (2)
* We filterd regions with regional minimum FDR of both genes and SNPs < 0.01, round 400 regions left.
* Susie run parameters: `L=1`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

```{r param4, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config4.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config4.susieI.txt")

# Plot PIP

Red is causal.

```{r gene twas, fig.height=4, fig.width=10}
chrom <- 1
tag <- "20201001-2-1"
pipfile <-  paste0(outputdir, tag, ".config2.1.SERI.txt")
a <- fread(pipfile, header = T)

plot(a[a$chr ==chrom, ]$pos, a[a$chr ==chrom, ]$SERpip, col = a[a$chr ==chrom, ]$ifcausal + 1, xlab = paste0("chr", chrom), ylab = "pip", pch = c(1,2)[as.factor(a[a$chr ==chrom, ]$type)])
points(a[a$chr ==chrom & a$ifcausal ==1, ]$pos, a[a$chr ==chrom & a$ifcausal ==1, ]$SERpip , col = "red", pch = c(19, 17)[as.factor(a[a$chr ==chrom & a$ifcausal ==1 , ]$type)])
legend("topright",c("gene","SNP"),cex=.8,pch=c(1,2))
grid()
```

>>>>

Next, the analysis is done at the “region” level, which is 500kb bins along the genome. We also used LDetect to define regions. We are exploring several ways to select regions that contain true signals, e.g. based on regional sum of mr.ash PIP for genes/SNPs, region smallest TWAS p value for gene/SNPs, or regional bayes factors, etc.

@@

## susieI
* Regions: all regions, 500kb uniform regions.
* Susie run parameters: `L=1`.  We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes). Prior variance and residual variance were calculated by SUSIE for each region.

```{r param1susie, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.susieI.txt")

##  Single effect model/EM (1)
* Regions: all regions, 500kb uniform regions.
* Run parameters: We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes). We use the true prior variance for genes and SNPs.

@@

##  Single effect model/EM (2)
* Regions: all regions, defined based on LDetect.
* Run parameters: We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes). We use the true prior variance for genes and SNPs.

```{r param6, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config6.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config6.SERI.txt")

@@

##  Single effect model/EM (3)
* Regions: regions with at most 1 causal signal, regions are defined based on LDetect.
* Run parameters: We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes). We use the true prior variance for genes and SNPs.

```{r param7, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config7.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config7.SERI.txt")

@@

### 2020-11-04 analysis/simulation-susieI-ukbWG-gtex.adipose_visual.Rmd
SERI

```{r sim 2-1-1, out.width = "98%", out.height="95%"}
chrom <- 1
tag <- "20201001-2-1"
pipfile <-  paste0(outputdir, tag, ".config2.1.SERI.txt")
phenof <- paste0(simdatadir, "simu_", tag, "-pheno.Rd")
plot_all(pipfile, phenof, chrom)
```

>>>>

```{r sim 2-1-1, out.width = "98%", out.height="95%"}
chrom <- 1
tag <- "20201001-2-1"
pipfile <-  paste0(outputdir, tag, ".config.1.SERI.txt")
phenof <- paste0(simdatadir, "simu_", tag, "-pheno.Rd")
plot_all(pipfile, phenof, chrom)
```
